Title

### 2018-08-01 thesis/paper/paper.tex
Added symmetric
Added multi-value

>>>>

\subsection{Symmetric (Q21510862)}
The symmetric constraint can be translated exactly as the inverse constraint if the inverse property where set to the same as the constrained property.

\subsection{Multi-value (Q21510857)}
The multi-value constraint requires a limited count of constrained statements. Alternatively, it could be said that if the item requires a second statement, the constraint is violated. Pre-processing extracts all items statements and inequality between all item statement properties as usual and the conjunction is \(t = \text{tripleEDB}(S, I, P, V) \wedge \text{unequal}(\text{propertyConstant}, P)\). The predicate require\_second\([2]\) is introduced with the same meaning as require except that it will be applied after a required property has been found:
\begin{equation*}
\text{require\_second}(S, \text{propertyConstant}) \leftarrow \text{next}(Q, R) \wedge \text{next}(R, S) \wedge \text{require}(Q) \wedge t
\end{equation*}
\begin{equation*}
\text{require\_second}(S, \text{propertyConstant}) \leftarrow \text{next}(R, S) \wedge \text{require\_second}(R) \wedge t
\end{equation*}
A violations would be any last statement requiring a second constrained statement.
